### 2019-06-19 thesis-template/msc-thesis.tex
update

The star example reveals another interesting feature of the approach: if the intensity impulsively hits an isotropic region, it gets split up into a range of the neighboring $180$ degrees of directions:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star-0,0.png}
    \label{a)}
    \caption*{single light src}
  \end{minipage}
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star-two-wide.png}
    \label{b)}
    \caption*{symmetric light src's}
  \end{minipage}
   \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star-two-dense.png}
    \label{c)}
    \caption*{dual light src's}
  \end{minipage}
\caption{final light propagation distributions for ``star''-test field}
\label{spiral-tests}
\end{figure}
This gets even clearer, when we plot the heat map depiction again:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star_wide.png}
    \label{a)}
    \caption*{symmetric light src's}
  \end{minipage}
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star_close.png}
    \label{b)}
    \caption*{dual light src's}
  \end{minipage}
\caption{final light propagation distributions for ``star''-test field}
\label{spiral-tests}
\end{figure}
Note that we skipped the single light source example, since we consider it a trivial add-on example. We can regard the intensities condensed inside of a narrow beam of light.
Note, that a logarithmic scale needs to be incorporated to produce results on a large scale in a sense of higher spatial resolution (e.g. $100x100$), since the propagation attenuation follows the distance to the origin inversely proportional.

\section{Behaviour for Total Anisotropy}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda_1>0$ and the other $\lambda_2=0$) incorporated. For this we set up bidirectional delta-pulses as transmission profiles to have the whole energy transmitted in just one, discrete direction.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field Lines and glyphs for ``rings''-Testfield, b) intensity propagation in grid}
\label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as the approach uses 8 discrete directions to propagate averaged intensity whereas the circle uses much more (namely infinite if presumed as perfect circle). Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter and escape each) as observable in Fig. \ref{anisotropy}. Nonetheless, the energies are transmitted in circular orbits around the circle center.	
\section{Energy Conservation Test}
\label{sect:conserve}
The energy conservation test was done in similar manner as thepropagation attenuation test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum (e.g. $\int_0^{2\pi}1\mathop{d\omega}=2\pi$) in iteration 0 in absolute values. This energetic error analysis yields the following graph depicted in Fig. \ref{energy}:

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}\bigskip
    \includegraphics[width=\textwidth]{img/drain(alt)-TFL.png}
    \label{a)}
    \caption{a) TFLs and glyphs for ``drain'' test field}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/ftle_drain_alt.png}
    \label{b)}
    \caption{b) LTG($90^\circ$) for a)}
  \end{minipage}
\label{anisotropy}
\end{figure}
What we can observe here, is a feature called a ``ridge'' occuring as a high value line segment (red vertical track) which is already quite obvious for human vision. A gradient filter could be applied to extract and emphasize edges from the image as a preprocessing step for computer vision, which would look like the following:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}\bigskip
    \includegraphics[width=\textwidth]{img/ftle_drain_alt.png}
    \label{a)}
    \caption{a) LTG($90^\circ$) for ``drain'' test field}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/drain_alt_gradient.png}
    \label{b)}
    \caption{b) gradient for a)}
  \end{minipage}
\label{anisotropy}
\end{figure}

>>>>

The star example reveals another interesting feature of the approach: if the intensity impulsively hits an isotropic region, it gets directed according to its intensity profile (neglecting the transmission profile) which implements the principle of inertia for directed light propagation present in vacuum (light never changes its direction):
\begin{figure}[!t]
\centering
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star-0,0.png}
    \label{a)}
    \caption*{single light src}
  \end{minipage}
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star-two-wide.png}
    \label{b)}
    \caption*{symmetric light src's}
  \end{minipage}
   \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star-two-dense.png}
    \label{c)}
    \caption*{dual light src's}
  \end{minipage}
\caption{final light propagation distributions for ``star'' test field}
\label{spiral-tests}
\end{figure}
Remark, that the diagonal intensities are attenuated more strongly by default, which introduces a bias into the light paths which are chosen along the axes with higher propability, effectively. This gets even clearer, when we plot the heat map depiction again:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star_wide.png}
    \label{a)}
    \caption*{symmetric light src's}
  \end{minipage}
  \begin{minipage}{0.31\textwidth}
    \includegraphics[width=\textwidth]{img/star_close.png}
    \label{b)}
    \caption*{dual light src's}
  \end{minipage}
\caption{final light propagation distributions for ``star'' test field}
\label{spiral-tests}
\end{figure}
Note that we skipped the single light source example, since we consider it a trivial add-on example. We can regard the intensities condensed inside of a narrow beam of light.
Note, that a logarithmic scale needs to be incorporated to produce results on a large scale in a sense of higher spatial resolution (e.g. $100x100$), since the propagation attenuation follows the distance to the origin inversely proportional.

\section{Behaviour for Total Anisotropy}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda_1>0$ and the other $\lambda_2=0$) incorporated. For this we set up bidirectional Dirac-pulses as transmission profiles to have the whole energy transmitted in just one, discrete direction.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field Lines and glyphs for ``rings''-Testfield, b) intensity propagation in grid}
\label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as the approach uses 8 discrete directions to propagate averaged intensity whereas the circle uses much more (namely infinite if presumed as perfect circle). Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter and escape each) as observable in Fig. \ref{anisotropy}. Nonetheless, the energies are transmitted in circular orbits around the circle center.	
\section{Energy Conservation Test}
\label{sect:conserve}
The energy conservation test was done in similar manner as thepropagation attenuation test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum (e.g. $\int_0^{2\pi}1\mathop{d\omega}=2\pi$) in iteration 0 in absolute values. This energetic error analysis yields the following graph depicted in Fig. \ref{energy}:

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}\bigskip
    \includegraphics[width=\textwidth]{img/drain(alt)-TFL.png}
    \label{a)}
    \caption{a) TFLs and glyphs for ``drain'' test field}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/ftle_drain_alt.png}
    \label{b)}
    \caption{b) LTG($90^\circ$) for a)}
  \end{minipage}
\label{anisotropy}
\end{figure}
What we can observe here, is a feature called a ``ridge'' occuring as a high value line segment (red vertical track) which is already quite obvious for human vision. A gradient filter could be applied to extract and segment edges from the image as a preprocessing step for computer vision, which would look like the image in Fig. \ref{gradb)}:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}\bigskip
    \includegraphics[width=\textwidth]{img/ftle_drain_alt.png}
    \label{grada)}
    \caption{a) LTG($90^\circ$) for ``drain'' test field}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/drain_alt_gradient.png}
    \label{gradb)}
    \caption{b) gradient for a)}
  \end{minipage}
\end{figure}
